\documentclass{article}
\usepackage{amsmath,amssymb,amsthm, fancyhdr, tikz-cd, xcolor}
\definecolor{mypink1}{rgb}{0.858, 0.188, 0.478}
\swapnumbers

\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{\thesubsection\ #1}}
\fancyhf{}
\lhead{Research Outline}
\rhead{Tony Martino}

\newtheoremstyle{mystyle}
  {\topsep}
  {\topsep}
  {}
  {}
  {\scshape}
  {.}
  {.5em}
  {}


\theoremstyle{mystyle}
\newtheorem{thm}{Theorem}[section]
\newtheorem{thm*}{Theorem}[section]
\newtheorem{lem}{Lemma}[section]
\newtheorem{pro}[lem]{Proposition}
\newtheorem{defn}[lem]{Definition}
\newtheorem*{defn*}{Definition}
\newtheorem*{claim*}{Claim}
\newtheorem*{lem*}{Lemma}

\theoremstyle{remark}
\newtheorem{rmk}[lem]{Remark}
\newtheorem{ex}[lem]{Example}
\newtheorem{nex}[lem]{Not Example}



\begin{document}
\section{Background}

\begin{enumerate}
    \item cohomological and geometric dimension
    \item group splittings
    \item Danny Wise VH-complexes
    
        In his thesis Danny Wise considered {\em VH-complexes}, these are square complexes with the edge set split into two disjoint sets such that attaching maps alternate between them. Among other items, Wise showed that from a VH-complex you can extract two splittings (vertical and horizontal respectively) of it's fundamental group.
    \item Guirardel Core
\end{enumerate}

\section{Problem Statement}

Statement for Dimension 2: 

Wise obtained splittings from a VH-complex, we want a kind of converse. Consider a group of cohomological dimension two that has two actions on locally finite trees with FP vertex stabilizers. Suppose further that these actions are not in the same deformation space. We want to conclude our group is the fundamental group of a compact VH-complex and moreover the actions coming from Wise's work recover our original actions.

To begin consider the diagonal action of our group on the tree product - a square complex, in fact it has a natural VH structure where vertical (horizontal) edges correspond to edges in the first (second) tree. The diagonal action preserves edges in each tree and so preserves the VH structure. We first need to show that this action is free. (...)

Once we have a free action we introduce the Guirardel core, an invariant, simply-connected, cocompact subcomplex of the tree product that depends on our two actions. This implies that we have the fundamental group of a compact VH-complex as needed.

Lastly, we want to recover our original actions. The two actions from Wise's work come from considering our complex as a graph of spaces where the edge spaces are roughly the hyperplanes crossing the vertical edges. Then similarly for horizontal edges. (That these hyperplanes are separating and injective on fundamental group comes from conditions verified by Wise, that they are two-sided follows from the fact that our tree actions are without edge inversions) With the vertical and horizontal actions in hand we need to show they match our original actions. (...)

\section{Progress}

\begin{enumerate}
    \item Freeness of product action:

	    We're going to walk through the setup in the two dimensional case. Let \(G\) be a group with two locally finite type \(FP\) actions \(T_{1}\) and \(T_{2}\) lying in different deformation spaces.  Consider the diagonal action on \(T_{1} \times T_{2}\), we will show that this action is free. {\color{mypink1}We will show that for a given \(g \in G\) that if \(g\) fixed a point in one tree then it doesn't fix a point in the other. By symmetry suppose \(g\) fixes a point in \(T_{1}\). Consider \(G_{v}\) where \(v\) lies in \(T_{1}\), as a subgroup of \(G\) it also acts on \(T_{2}\). Suppose that \(G_{v}\) acts without a global fixed point on \(T_{2}\) then }
    \item Hyperplane separability:
        Note that hyperplanes in the tree product are dual to edges in its one-skeleton and we have a diagonal action without edge inversions.
    \item Using Bieri: If a group \(G\) has geometric dimension \(n\) and acts on a locally finite tree with \(FP_\infty\) (i.e. finite dimensional \(K(G,1)\)) stabilizers then the stabilizers have geometric dimension \(\leq n-1\).
    \item Using Howsen
    \item Using ``Quadrant-Convex'' lemma of Guirardel 
    \item Using injectivity lemma for maps of NPC complexes
    \item other: relevant facts on locally finite trees
\end{enumerate};

\end{document}
\section{Guirardel Core}

\section{VH-complexes}

Let \(X\) be our complex and \(X_{V}\) be the set of vertical edges. We say gates are connected components of \(X_{V}\) and corridors are cc of \(X - X_{V}\). The complex \(X\) is clean if the attaching maps of the corridors are injective.

\begin{thm}[Wise]
	If \(X\) a complete, VH, clean, connected complex then there is a finite sheeted cover that's a graph product.
\end{thm}

\begin{thm}
	If \(X\) is NPC, VH, compact, nice(???) then \(X\) is complete XOR contains a locally geodesic VH pair of lollipops
\end{thm}

\section{Definitions}
\begin{defn}[Graph - Abstract]
	An {\em Abstract Graph} \(\Gamma\) is a set \((V,E, \partial, i)\) where \(V\) and \(E\) are non-empty sets and \(\partial: E \to V\) and \(i: E \to E\) are functions satisfying \(i^2(e)=e\) and \(i(e) \neq e\) for all \(e \in E\). (i.e. the function \(i\) is a fixed-point free involution)
	
\end{defn}

We set \(o(e) := \partial(e)\) and \(t(e) := (\partial\circ i)(e)\) for origin and terminal vertices and put \(\overline{e} := i(e)\). We call the orbits of \(i\) the {\em undirected edges} of \(G\). (i.e. the set \(\{ e, \overline{e}\}\) is an undirected edge) 

\begin{defn}
	A tree action \((G,T)\) is {\em minimal} if it contains no proper invariant subtree. A graph of groups \(\mathcal{G}\) is minimal if there is no proper subgroup carrying the entire group.
	
\end{defn}


\begin{defn}[Collapse Move]
	If we have a group \(G\) acting on a tree \(T\) with an edge \(e\) such that \(G_{e} = G_{v}\) where \(v=o(e)\) and \(o(e)\) and \(t(e)\) are in different \(G\)-orbits then we can form \(T_{e}\) a new tree with \(V(T_{e} )=V(T)\smallsetminus G t(e)\) and \(E(T_{e} )=E(T) \smallsetminus Ge\). Then for all edges \(f\) with \(o(f) = t(ge)\) for some \(g \in G\) we define \(o(f)=gv\) in \(T_{e}\). 
	
	(Alternatively, if \(q\) was the map that paired the inital and terminal vertices of \(g e\) and left the others alone then we could define the new tree by taking \(E(T_{e} ):=E(T)\smallsetminus Ge \) and \(V(T_{e} ):=q(V)\) with attaching map \(q \circ \partial\).

	If \(\mathcal{G}\) is a graph of groups decomposition of \(G\) with \(\varphi_{e}: G_{e} \to G_{\partial e}\) an isomorphism then define \(\mathcal{G}_{e}\) by removing \(e\), \(\overline{e}\) and \(\partial e\) and for every edge \(f\) with \(\partial(f) = \partial(e)\) replace \(\varphi_{f}\) with \(\varphi_{\overline{e}} \circ \varphi_{e}^{-1} \circ \varphi_{f}\) and set \(\partial f = \partial \overline{e}\). This corresponds to taking the edge \(e\) from the tree description above and folding \([e]\) in the graph.

\end{defn}
\begin{defn}[Fold]
	Given a tree with \(\partial e = \partial f\) identify \(e\) with \(f\) as well as \(\overline{e}\) and \(\overline{f}\) and \(\overline{\partial} e\) with \(\overline{\partial} f\) and do so equivariantly. (In \(\mathcal{G}\) this corresponds to moves of type A or B with subtype I, II, or III.)
\end{defn}

\begin{claim*} A reduced not locally finite tree remains not locally finite after folding.
\end{claim*}

\hrulefill

\section{Claims}



\end{document}
